Results

### 2018-07-16 02_analysis.Rmd
Calculate percent change!

# Load data
results <- readRDS(file.path(here(), "data", "results_clean.rds"))

@@

plot_donate_summary

@@

pairs_plot_data_c <- diffs_coef_pairs_c %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

@@

pairs_plot_data_i <- diffs_coef_pairs_i %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))
```

@@

pairs_plot_data_f <- diffs_coef_pairs_f %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))
```

@@

# All the pairwise differences in a single data frame, grouped by issue
pairs_conditions_ci <- all_chains_ci %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))

# Extract coefficient details and plot data
diffs_coef_pairs_detail_ci <- pairs_conditions_ci %>% 
  unnest(diffs_coef_pairs_detail) %>% 
  select(-data, -diffs_coef_pairs)

pairs_plot_data_ci <- pairs_conditions_ci %>% 
  select(issue, diffs_coef_pairs) %>% 
  unnest(diffs_coef_pairs) %>%
  gather(pair, value, -issue) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

@@

# All the pairwise differences in a single data frame, grouped by issue
pairs_conditions_cif <- all_chains_cif %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))

# Extract coefficient details and plot data
diffs_coef_pairs_detail_cif <- pairs_conditions_cif %>% 
  unnest(diffs_coef_pairs_detail) %>% 
  select(-data, -diffs_coef_pairs)

pairs_plot_data_cif <- pairs_conditions_cif %>% 
  select(issue, funding, diffs_coef_pairs) %>% 
  unnest(diffs_coef_pairs) %>%
  gather(pair, value, -issue, -funding) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

@@

diffs_coef_pairs_detail_singles <- bind_rows(diffs_coef_pairs_detail_c,
                                             diffs_coef_pairs_detail_i,
                                             diffs_coef_pairs_detail_f) %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair),
         pair = fct_inorder(pair, ordered = TRUE))

@@

```{r tbl-single-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_i,
          diffs_coef_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:amount-single-diffs}") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-single-diffs.md"))
```

@@

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions {#tbl:amount-diffs}') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-diffs.md"))
```

@@

pairs_likely_plot_data_c <- diffs_coef_likely_pairs_c %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

@@

pairs_likely_plot_data_i <- diffs_coef_likely_pairs_i %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))
```

@@

pairs_likely_plot_data_f <- diffs_coef_likely_pairs_f %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))
```

@@

# All the pairwise differences in a single data frame, grouped by issue
pairs_likely_conditions_ci <- all_chains_likely_ci %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))

@@

pairs_likely_plot_data_ci <- pairs_likely_conditions_ci %>% 
  select(issue, diffs_coef_pairs) %>% 
  unnest(diffs_coef_pairs) %>%
  gather(pair, value, -issue) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

@@

# All the pairwise differences in a single data frame, grouped by issue
pairs_likely_conditions_cif <- all_chains_likely_cif %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)))

# Extract coefficient details and plot data
diffs_coef_likely_pairs_detail_cif <- pairs_likely_conditions_cif %>% 
  unnest(diffs_coef_pairs_detail) %>% 
  select(-data, -diffs_coef_pairs)

pairs_likely_plot_data_cif <- pairs_likely_conditions_cif %>% 
  select(issue, funding, diffs_coef_pairs) %>% 
  unnest(diffs_coef_pairs) %>%
  gather(pair, value, -issue, -funding) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " − ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair))

plot_diffs_likely_cif <- ggplot() + 
  geom_density(data = pairs_likely_plot_data_cif, aes(x = value),
               fill = ngo_cols("red"), colour = NA, alpha = 0.4) + 
  geom_segment(data = diffs_coef_likely_pairs_detail_cif, 
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_cif, 
             aes(xintercept = median), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  scale_x_continuous(labels = percent) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + funding + pair)
```

@@

diffs_coef_likely_pairs_detail_singles <- bind_rows(diffs_coef_likely_pairs_detail_c,
                                                    diffs_coef_likely_pairs_detail_i,
                                                    diffs_coef_likely_pairs_detail_f) %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "−", "−\n"),
                       pair),
         pair = fct_inorder(pair, ordered = TRUE))

@@

```{r tbl-single-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_i,
          diffs_coef_likely_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:likelihood-single-diffs}") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-single-diffs.md"))
```

@@

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions {#tbl:likelihood-diffs}') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-diffs.md"))
```

>>>>

# Load data
results <- readRDS(file.path(here(), "data", "results_clean.rds"))
# qwraps2::lazyload_cache_dir("02_analysis_cache/html")

@@

@@

pairs_plot_data_c <- diffs_coef_pairs_c$mcmc_diffs %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair))

@@

pairs_plot_data_i <- diffs_coef_pairs_i$mcmc_diffs %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair))
```

@@

pairs_plot_data_f <- diffs_coef_pairs_f$mcmc_diffs %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair))
```

@@

# All the pairwise differences in a single data frame, grouped by issue
pairs_conditions_ci <- all_chains_ci %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)),
         diffs_coefs = diffs_coef_pairs %>% map(~ .$mcmc_diffs))

# Extract coefficient details and plot data
diffs_coef_pairs_detail_ci <- pairs_conditions_ci %>% 
  unnest(diffs_coef_pairs_detail) %>% 
  select(-data, -diffs_coef_pairs, -diffs_coefs) #%>% 
  #mutate(pair = "Hey")

pairs_plot_data_ci <- pairs_conditions_ci %>% 
  select(issue, diffs_coefs) %>% 
  unnest(diffs_coefs) %>%
  gather(pair, value, -issue) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair))

@@

# All the pairwise differences in a single data frame, grouped by issue
pairs_conditions_cif <- all_chains_cif %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)),
         diffs_coefs = diffs_coef_pairs %>% map(~ .$mcmc_diffs))

# Extract coefficient details and plot data
diffs_coef_pairs_detail_cif <- pairs_conditions_cif %>% 
  unnest(diffs_coef_pairs_detail) %>% 
  select(-data, -diffs_coef_pairs, -diffs_coefs)

pairs_plot_data_cif <- pairs_conditions_cif %>% 
  select(issue, funding, diffs_coefs) %>% 
  unnest(diffs_coefs) %>%
  gather(pair, value, -issue, -funding) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair))

@@

diffs_coef_pairs_detail_singles <- bind_rows(diffs_coef_pairs_detail_c,
                                             diffs_coef_pairs_detail_i,
                                             diffs_coef_pairs_detail_f) %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair),
         pair = fct_inorder(pair, ordered = TRUE))

@@

```{r tbl-single-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_i,
          diffs_coef_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:amount-single-diffs}") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-single-diffs.md"))
```

@@

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `Crackdown - No crackdown~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between amounts donated in "crackdown" (treatment) and "no crackdown" (control) conditions {#tbl:amount-diffs}') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-diffs.md"))
```

@@

pairs_likely_plot_data_c <- diffs_coef_likely_pairs_c$mcmc_diffs %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair))

@@

pairs_likely_plot_data_i <- diffs_coef_likely_pairs_i$mcmc_diffs %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair))
```

@@

pairs_likely_plot_data_f <- diffs_coef_likely_pairs_f$mcmc_diffs %>%
  gather(pair, value) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair))
```

@@

# All the pairwise differences in a single data frame, grouped by issue
pairs_likely_conditions_ci <- all_chains_likely_ci %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)),
         diffs_coefs = diffs_coef_pairs %>% map(~ .$mcmc_diffs))

@@

pairs_likely_plot_data_ci <- pairs_likely_conditions_ci %>% 
  select(issue, diffs_coefs) %>% 
  unnest(diffs_coefs) %>%
  gather(pair, value, -issue) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair))

@@

# All the pairwise differences in a single data frame, grouped by issue
pairs_likely_conditions_cif <- all_chains_likely_cif %>% 
  mutate(diffs_coef_pairs = data %>% map(~ mcmc_pairwise_diffs(.)),
         diffs_coef_pairs_detail = diffs_coef_pairs %>% map(~ tidy_diffs(.)),
         diffs_coefs = diffs_coef_pairs %>% map(~ .$mcmc_diffs))

# Extract coefficient details and plot data
diffs_coef_likely_pairs_detail_cif <- pairs_likely_conditions_cif %>% 
  unnest(diffs_coef_pairs_detail) %>% 
  select(-data, -diffs_coef_pairs, -diffs_coefs)

pairs_likely_plot_data_cif <- pairs_likely_conditions_cif %>% 
  select(issue, funding, diffs_coefs) %>% 
  unnest(diffs_coefs) %>%
  gather(pair, value, -issue, -funding) %>%
  mutate(pair1 = pair) %>%
  separate(pair1, into = c("group1", "group2"), sep = " - ") %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair))

plot_diffs_likely_cif <- ggplot() +
  geom_density(data = pairs_likely_plot_data_cif, aes(x = value),
               fill = ngo_cols("red"), colour = NA, alpha = 0.4) +
  geom_segment(data = diffs_coef_likely_pairs_detail_cif,
               aes(x = q5, xend = q95, y = 0, yend = 0),
               size = 3) +
  geom_vline(data = diffs_coef_likely_pairs_detail_cif,
             aes(xintercept = `median`), size = 0.25) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  guides(fill = FALSE, color = FALSE) +
  scale_x_continuous(labels = percent) +
  labs(x = "Difference in medians") +
  theme_ngos(density = TRUE) +
  facet_wrap(~ issue + funding + pair)
```

@@

diffs_coef_likely_pairs_detail_singles <- bind_rows(diffs_coef_likely_pairs_detail_c,
                                                    diffs_coef_likely_pairs_detail_i,
                                                    diffs_coef_likely_pairs_detail_f) %>%
  mutate(pair = ifelse(nchar(pair) > 25,
                       str_replace(pair, "-", "-\n"),
                       pair),
         pair = fct_inorder(pair, ordered = TRUE))

@@

```{r tbl-single-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_i,
          diffs_coef_likely_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:likelihood-single-diffs}") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-single-diffs.md"))
```

@@

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `Crackdown - No crackdown~median~` = median, 
         `% change~median~` = median_pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between likelihood to donate in "crackdown" (treatment) and "crackdown" (control) conditions {#tbl:likelihood-diffs}') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-diffs.md"))
```
